Tropical Andes Functional diversity for plants and Frugivores

### 2024-05-22 code/L2/L2_1_TropicalAndes_funcdiv.Rmd
re-order mapping code

@@

## Project FD objects
```{r}
# Generate coordinates
subset_coords_frugivore <- site_loc_key_frugivore[rowSums(PAM_frugivore_site_final) >= 5, ]
subset_coords_frugivore_sp <-subset_coords_frugivore[,1:2 ]

```{r}
spatial_fdis_frugivore_projected <- st_transform(spatial_fdis_frugivore, 5389)
```

```{r}
create_fdis_plots <- function(resolution_meters, data, variable_name) {
# Make Grid
TAGrid <- TApoly %>%
  st_make_grid(cellsize = c(resolution_meters)) %>%
  st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
  st_cast("MULTIPOLYGON") %>%
  st_sf() %>%
  mutate(cellid = row_number())

  # Calculate functional dispersion for grid
  fdis_grid <- TAGrid %>%
    st_join(data) %>%
    group_by(cellid) %>%
    summarize(
      sum_variable = sum(variable_name, na.rm = TRUE),
      mean_variable = mean(variable_name, na.rm = TRUE)
    )

  # Make plot
  FDplot <-
    ggplot() +
    geom_sf(data = Americas, fill = "white")+
    geom_sf(data = TApoly, fill = "lightgrey", size = 0.1) +
    geom_sf(data = fdis_grid, aes(fill = fdis_frugivore)) +
    scale_fill_gradient(low = "blue", high = "red") +
    coord_sf(xlim = c(-82, -60), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    theme(panel.background = element_rect(fill = "lightblue")) +
    annotation_scale(location = "bl", width_hint = 0.5) +
    labs(x = "Longitude", y = "Latitude", fill = "FDis")

  # Return a list of data
  list(fdis_grid = fdis_grid,
        FDplot = FDplot)
}
```

```{r}
create_fdis_plots(100000, spatial_fdis_frugivore_projected, fdis_frugivore)
```

>>>>

## Mapping FD

@@
